An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-09 paper.tex
Minor edits.

\begin{listing*}
  \begin{minted}{python}
    >>> from gaitanalysis.motek import DFlowData
    >>> data = DFlowData('mocap-020.txt', 'record-020.txt', 'meta-020.yml')
    >>> mass = data.meta['subject']['mass']
    >>> data.clean()
    >>> event_df = dflow_data.extract_processed_data(event='Longitudinal Perturbation')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing*}

@@

\begin{listing*}
  \begin{minted}{python}
    >>> from gaitanalysis.gait import GaitData
    >>> gdata = GaitData(event_df)
    >>> gdata.inverse_dynamics_2d(left_markers, right_markers, left_loads,
    ...                           right_loads, mass, 6.0)
    >>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
    >>> gdata.split_at('right')
    >>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
    >>> gdata.save('gait-data.h5')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could compute
    the inverse dynamics (joint angles and torques), indentify the gait
    landmarks (e.g. heelstrikes), split the data with respect to the gait
    landmarks in a Pandas \verb|Panel|, plot the mean and standard deviation of
    one time history with respect to the gait cycles, and save the data to disk.}
  \label{lis:dflowdata}
\end{listing*}

@@

\subsection*{Author contributions}
A.v.d.B. conceived of the experiments and protocol. J.K.M and S.K.H developed
the protocol, ran the experiments, and collected the data. J.K.M was the
primary author of the paper with significant contributions from S.K.H and
A.v.d.B. All authors were involved in the revision of the draft manuscript and
have agreed to the final content.

>>>>

\begin{listing*}
  \begin{minted}[gobble=4]{python}
    >>> from gaitanalysis.motek import DFlowData
    >>> data = DFlowData('mocap-020.txt', 'record-020.txt', 'meta-020.yml')
    >>> mass = data.meta['subject']['mass']
    >>> data.clean_data()
    >>> event_df = dflow_data.extract_processed_data(event='Longitudinal Perturbation')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could load a
    trial into memory, extract the subject's mass from the meta data, run the
    data cleaning process, and finally extract a Pandas \verb|DataFrame|
    containing all of the time histories for a specific event in the trial.}
  \label{lis:dflowdata}
\end{listing*}

@@

\begin{listing*}
  \begin{minted}[gobble=4]{python}
    >>> from gaitanalysis.gait import GaitData
    >>> gdata = GaitData(event_df)
    >>> gdata.inverse_dynamics_2d(left_markers, right_markers, left_loads,
    ...                           right_loads, mass, 6.0)
    >>> gdata.grf_landmarks('Right Fy', 'Left Fy', threshhold=20.0)
    >>> gdata.split_at('right')
    >>> gdata.plot_gait_cycles('Left Hip Joint Torque', mean=True)
    >>> gdata.save('gait-data.h5')
  \end{minted}
  \cprotect\caption{Python interpreter session showing how one could compute
    the inverse dynamics (joint angles and torques), indentify the gait
    landmarks (e.g. heelstrikes), split the data with respect to the gait
    landmarks in a Pandas \verb|Panel|, plot the mean and standard deviation of
    one time history with respect to the gait cycles, and save the data to disk.}
  \label{lis:dflowdata}
\end{listing*}

@@

\subsection*{Author contributions}
A.v.d.B. conceived of the experiments and protocol. J.K.M and S.K.H refined the
protocol, ran the experiments, and collected the data. J.K.M was the primary
author of the paper with significant contributions from S.K.H and A.v.d.B. All
authors were involved in the revision of the draft manuscript and have agreed
to the final content.
